\documentclass[10pt]{article}
\usepackage{graphicx}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.06cm,top=1.1cm,right=1.06cm,bottom=0.49cm]{geometry}

\usepackage{multicol}
\usepackage{xcolor}
\definecolor{mylinkcolor}{RGB}{0,71,171}
\hypersetup{
	colorlinks=false,
	hidelinks,
}

\setlength{\parskip}{0pt}
% Tighter centered section-title blocks
\let\oldcenter\center
\let\oldendcenter\endcenter
\renewenvironment{center}{\setlength{\topsep}{1pt}\setlength{\partopsep}{0pt}\oldcenter}{\oldendcenter}

\begin{document}
	\begin{center}
		\textbf{\Large Yiquan Wang}\\
		\textbullet \ +86-19537838515 \textbullet \ \textcolor{mylinkcolor}{\href{mailto:ethan@stu.xju.edu.cn}{ethan@stu.xju.edu.cn}} \textbullet \ \textcolor{mylinkcolor}{\href{https://wyqmath.cn/}{Homepage}} \textbullet \ \textcolor{mylinkcolor}{\href{https://github.com/wyqmath}{GitHub}} \textbullet \ \textcolor{mylinkcolor}{\href{https://scholar.google.com/citations?user=ULP3e1cAAAAJ}{Google Scholar}} \textbullet \ \textcolor{mylinkcolor}{\href{https://orcid.org/0000-0003-1417-5752}{ORCID}} \textbullet \ \textcolor{mylinkcolor}{\href{https://openreview.net/profile?id=~Yiquan_Wang3}{OpenReview}} \\
		\textbullet \ Member of IEEE Biometrics Council, Chinese Chemical Society \& Biophysical Society of China \\
		\hrulefill
	\end{center}
	
	\vspace{1pt}
	
	\begin{center}
		\textbf{\large Education}
	\end{center}
	\textbf{\textcolor{black}{\href{https://math.xju.edu.cn/}{National Base for Mathematical Research and Teaching Talents}}, \textcolor{black}{\href{https://www.xju.edu.cn/}{Xinjiang University}}} \hfill Urumqi, Xinjiang \\
	{\small \textit{B.S. in Mathematics and Applied Mathematics}} \hfill 2023.09 – 2027.06

	\vspace{4pt}

	\textbf{\textcolor{black}{\href{https://www.teep.cnmm.tsinghua.edu.cn/}{Tsien Excellence in Engineering Program}}, \textcolor{black}{\href{https://www.tsinghua.edu.cn/}{Tsinghua University}} \& \textcolor{black}{\href{https://www.x-institute.edu.cn/}{Shenzhen X-Institute}}} \hfill Shenzhen, Guangdong \\
	{\small \textit{Joint Program, X Scholar} --- Representation learning for protein function and dynamics} \hfill 2024.06 – 2027.06

	\vspace{4pt}

	\textbf{\textcolor{black}{\href{https://szbl.ac.cn/research/institutes/INPD.htm}{Institute of Neurological and Psychiatric Disorders}}, \textcolor{black}{\href{https://www.szbl.ac.cn/}{Shenzhen Bay Laboratory}}} \hfill Shenzhen, Guangdong \\
	{\small \textit{Visiting Student, \textcolor{black}{\href{https://www.szbl.ac.cn/research/group/Wen-Yuan.htm}{Wen Yuan's Research Group}}} --- Single-cell bioinformatics for neurobiology studies} \hfill 2025.07 – 2025.09

	\vspace{4pt}

	\textbf{\textcolor{black}{\href{https://en.szbl.ac.cn/research/institutes/ISPB.htm}{Institute of Systems and Physical Biology}}, \textcolor{black}{\href{https://www.szbl.ac.cn/}{Shenzhen Bay Laboratory}}} \hfill Shenzhen, Guangdong \\
	{\small \textit{Visiting Student, \textcolor{black}{\href{https://www.szbl.ac.cn/research/group/Kai-Huang.htm}{Kai Huang's Research Group}}} --- IDP, LLPS \& genome folding, undruggable-target design} \hfill Starting 2026.07

	\vspace{5pt}

	\begin{center}
		\textbf{\large Selected Publications}
	\end{center}
	{\small \textit{Name in bold; $\dagger$ co-first author; * corresponding author.}}

	\textbf{Direction 1: Representation Learning \& Biomolecular Mechanisms}
	\begin{enumerate}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*, label={[\arabic*]}]
		\item \textbf{Wang, Y.}, et al. (2025). \textcolor{black}{\href{https://pubs.acs.org/doi/10.1021/acs.jcim.5c01768}{From Signal to Symphony: Exploring 2D Sequence Representations for Protein Function Prediction}}. \textit{Journal of Chemical Information and Modeling}.
		\item \textbf{Wang, Y.*}, et al. (2026). \textcolor{black}{\href{https://openreview.net/forum?id=rTO3JOgC3a}{Sequence-context-aware decoding enables robust reconstruction of protein dynamics from crystallographic B-factors}}. \textit{Learning Meaningful Representations of Life (LMRL) Workshop at ICLR 2026}.
		\item \textbf{Wang, Y.*}, et al. (2026). Integrative transcriptomics, machine learning, and molecular docking derive a DAM-like macrophage signature for risk stratification and therapeutic nomination in glioblastoma. \textit{Computational Biology and Chemistry}.
		\item \textbf{Wang, Y.†}, et al. (2025). \textcolor{black}{\href{https://www.mdpi.com/2079-7837/14/12/1665}{Diffusion Models at the Drug Discovery Frontier: A Review on Generating Small Molecules versus Therapeutic Peptides}}. \textit{Biology}.
		\item Wang, X.†*, \textbf{Wang, Y.†*}, et al. (2025). \textcolor{black}{\href{https://ieeexplore.ieee.org/abstract/document/11356718/}{Octopus Inspired Optimization (OIO): A Hierarchical Framework for Navigating Protein Fitness Landscapes}}. \textit{In 2025 IEEE International Conference on Bioinformatics and Biomedicine (BIBM)}. IEEE.
		\item \textbf{Wang, Y.*}, et al. (2026). \textcolor{black}{\href{https://advanced.onlinelibrary.wiley.com/doi/full/10.1002/advs.74610}{Comment on: ``GLM7 – A Novel Composite Glycolipid Index Derived from Routine Health Indicators for Enhanced Diagnosis and Prediction of Multimorbidity''}}. \textit{Advanced Science}. (correspondence).
		\item \textbf{Wang, Y.*}, et al. (2025). \textcolor{black}{\href{https://www.jocn-journal.com/article/S0967-5868(25)00332-7/fulltext}{AI for disease prediction: Performance insights and key limitations}}. \textit{Journal of Clinical Neuroscience}. (correspondence).
	\end{enumerate}

	\vspace{3pt}

	\textbf{Direction 2: First-Principles of Biological Complexity Based on Mathematical Physics}
	\begin{enumerate}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*, label={[\arabic*]}, resume]
		\item \textbf{Wang, Y.*} (2026). \textcolor{black}{\href{https://arxiv.org/abs/2602.21787}{Sub-residue sharpness of protein helix-coil transitions reveals a spatial-spectral uncertainty limit}}. \textit{arXiv preprint arXiv:2602.21787}.
		\item \textbf{Wang, Y.*} (2026). \textcolor{black}{\href{https://arxiv.org/abs/2602.16255}{Piecewise integrability of the discrete Hasimoto map for analytic prediction and design of helical peptides}}. \textit{arXiv preprint arXiv:2602.16255}.
		\item \textbf{Wang, Y.*} (2026). \textcolor{black}{\href{https://arxiv.org/abs/2602.13160}{Structural barriers of the discrete Hasimoto map applied to protein backbone geometry}}. \textit{arXiv preprint arXiv:2602.13160}.
	\end{enumerate}

	\vspace{3pt}

	\textbf{Direction 3: Interdisciplinary Explorations \& Collaborative Synergies}
	\begin{enumerate}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*, label={[\arabic*]}, resume]
		\item \textbf{Wang, Y.}, Zai, J., Liu, Z., Chen, J., \& Sabir, E.* (2026). Hamiltonian Connectivity in $k$-Ary $n$-Cubes under a Region-Based Fault Model. \textit{Information Sciences}.
		\item \textbf{Wang, Y.*}, et al. (2026). \textcolor{black}{\href{https://www.sciencedirect.com/science/article/pii/S1474706526002937}{AI Driven Discovery of Bio Ecological Mediation in Cascading Heatwave Risks}}. \textit{Physics and Chemistry of the Earth}.
		\item \textbf{Wang, Y.*}, et al. (2026). \textcolor{black}{\href{https://www.biorxiv.org/content/10.64898/2026.01.31.702997.full}{Geometric Fragility in Alzheimer's Disease: Probing the Loss of Hippocampal Hierarchical Abstraction via Contrastive Point Cloud Modeling}}. \textit{In 2026 IEEE International Conference on Systems, Man, and Cybernetics (SMC)}. IEEE.
		\item Cai, M., \ldots, \textbf{Wang, Y.*}, \& Wei, K.* (2025). \textcolor{black}{\href{https://www.frontiersin.org/journals/aging-neuroscience/articles/10.3389/fnagi.2026.1847611}{APOE $\varepsilon$4-Associated Hippocampal Atrophy Trajectories Across the Alzheimer's Disease Continuum: A Systematic Review, Meta-Analysis, and Longitudinal Validation}}. \textit{Frontiers in Aging Neuroscience}.
	\end{enumerate}

	\vspace{5pt}

	\begin{center}
		\textbf{\large Research Projects}
	\end{center}
	\textbf{Tsinghua University Tsien Excellence in Engineering Program ESRT} \hfill 2024.08-2025.10
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item \textbf{Project:} From Signal to Symphony: Exploring 2D Sequence Representations for Protein Function Prediction.
		\item {\small Motivated by an intuition that protein structure mirrors music---catalytic sites resembling melodic climaxes and $\beta$-sheets resembling calmer passages---I encoded amino acid sequences as 2D spectrograms (protein sonification) for function prediction. Ablations across an 18{,}000-sequence/12-class benchmark showed the 1D$\to$2D representational structure itself, rather than explicit biophysical priors, was the key driver of performance, matching ESM-2 and ProtBERT and reaching 90.44\% on the external CARE benchmark.}
		\item {\small \textcolor{mylinkcolor}{\href{https://github.com/wyqmath/Symphony_of_Fate}{Project Repository}}. Supervised by Prof. \textcolor{mylinkcolor}{\href{https://scholar.google.com/citations?user=LLj__mMAAAAJ}{Kai Wei}}.}
	\end{itemize}

	\vspace{4pt}

	\textbf{Chinese Academy of Sciences (CAS) Innovation Practice Training Program} \hfill 2024.11 -- 2025.09
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item \textbf{Project:} A Knowledge Graph-based Q\&A System for Heatwave Disaster Adaptation.
		\item {\small Built HeDA, an autonomous synthesis agent that constructs a knowledge graph (34{,}933 entities, 42{,}890 relations) from 8{,}365 publications to map compound-heatwave cascading risks. On a temporally held-out multi-hop benchmark, graph augmentation improved accuracy by 8.1--9.8\% over standalone foundation models; topological analysis surfaced a bio-ecological mediation effect, where biological systems act as the primary structural mediators transforming physical hazards into systemic socioeconomic losses.}
		\item {\small \textcolor{mylinkcolor}{\href{https://github.com/wyqmath/heatwave}{Project Repository}}. Supervised by Researcher \textcolor{mylinkcolor}{\href{https://scholar.google.com/citations?user=OQDwnVUAAAAJ}{Yong Ge}}.}
	\end{itemize}

	\vspace{4pt}

	\textbf{Provincial Undergraduate Innovation Training Program} \hfill 2024.03 -- 2025.06
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item \textbf{Project:} Research on the Generation Cyclability of Cartesian Product Graphs and Related Problems.
		\item {\small Studied Hamiltonicity of the $k$-ary $n$-cube $Q_n^k$, a classical graph-theoretic interconnection topology. Motivated by the fact that real-world faults are spatially clustered rather than independent, I introduced the Region-Based Fault (RBF) model characterizing faults as connected subgraphs, and gave a constructive proof that $Q_n^k$ remains Hamiltonian-connected for odd $k \geq 3$, $n \geq 2$ under RBF conditions, via an adaptive graph-decomposition argument robust well beyond its theoretical guarantees.}
		\item {\small \textcolor{mylinkcolor}{\href{https://github.com/wyqmath/Hamiltonian_Path}{Project Repository}}. Supervised by Prof. \textcolor{mylinkcolor}{\href{https://orcid.org/0000-0003-1456-4539}{Eminjan Sabir}}.}
	\end{itemize}

	\vspace{4pt}

	\textbf{National Undergraduate Innovation Program} \hfill 2025.05 -- 2026.12
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item \textbf{Project:} Conditional Diffusion Model on Copy Number Variation for Alzheimer's Disease Risk Assessment.
	\end{itemize}

	\vspace{4pt}

	\textbf{Tsinghua University Tsien Excellence in Engineering Program ORIC} \hfill 2025.12 -- 2026.12
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item \textbf{Project:} Application of Artificial Intelligence in Whole Genome Selection Breeding.
	\end{itemize}

	\vspace{4pt}

	\textbf{Chinese Academy of Sciences (CAS) Innovation Practice Training Program} \hfill 2025.11 -- 2026.11
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item \textbf{Project:} Urban Big Data, Multimodal Fusion and Spatial Intelligence Analysis (Second Author).
	\end{itemize}

	\vspace{5pt}
	
	\begin{center}
		\textbf{\large Professional Experience}
	\end{center}
	\textbf{Beijing Frontier Research Center for Biological Structure, Tsinghua University} \hfill Beijing, China
	
	\textit{Intern} \hfill 2025.07 – Present
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item Developed the \textcolor{mylinkcolor}{\href{https://www.fbs.frcbs.tsinghua.edu.cn/competition/2025Peptide/}{Peptide Design Competition Website}}, the \textcolor{mylinkcolor}{\href{https://www.frcbs.tsinghua.edu.cn/cpdb/}{Polypeptide Structure Database}} and engaged in protein and polypeptide design research. Supervised by Prof. Yafei Yuan and \textcolor{mylinkcolor}{\href{https://wanggroup.ai/}{Prof. Tong Wang}}.
	\end{itemize}
	
	\vspace{4pt}
	
	\textbf{Institute of Software, CAS \& Huawei Mindspore Community} \hfill Remote
	
	\textit{Intern} \hfill 2024.09 – 2025.03
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item Implemented a VGG19-based model for Pollock-style art generation, focusing on fractal and turbulent feature extraction and the creation of NFT-based digital labels. Featured on \href{https://mp.weixin.qq.com/s/_N5oLsa0etJTxEOKRTt_4w}{Huawei's official Wechat}.
	\end{itemize}
	
	\vspace{4pt}

	\vspace{5pt}

	\begin{center}
		\textbf{\large Awards \& Honors}
	\end{center}
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item \textbf{China Undergraduate Life Science Contest}: National Second Prize \hfill 2026
		\item \textbf{``Challenge Cup'' China College Students' Extracurricular Academic Science and Technology Works Competition}:\\
		Autonomous Region Second Prize \hfill 2026
		\item \textbf{China College Students' E-Commerce ``Innovation, Creativity and Entrepreneurship'' Challenge}:\\
		Autonomous Region Second Prize \hfill 2026
		\item \textbf{China College Student Self-improvement Star} \hfill 2025
		\item \textbf{UN Global Leadership and ESG Programme $\times$ X-Institute Shenzhen "AI for the Young and the Elderly" Challenge}:\\
		Best Innovation Award \hfill 2026
		\item \textbf{Smart Chemical City Challenge (Xinjiang Station)}: Second Prize \hfill 2025
		\item \textbf{Contemporary Undergraduate Mathematical Contest in Modeling (CUMCM)}: National Second Prize \hfill 2025
		\item \textbf{SynBio Challenges}: Silver Award $\times$ 2 \hfill 2025
		\item \textbf{2025 X-Fusion "Global Innovator Fusion Conference"}: Best Poster Award \hfill 2025
		\item \textbf{The Mathematical Contest in Modeling (MCM)}: Honorable Mention \hfill 2025
		\item \textbf{Alibaba Cloud Tianchi University Student Competition}: National Finals, 17th Place \hfill 2024
		\item \textbf{APMCM Asia-Pacific Mathematical Modeling Competition}: National Third Prize \hfill 2024
	\end{itemize}

	\begin{center}
		\textbf{\large Academic Activities}
	\end{center}
		\textbf{Peer Reviewer:} ICLR/ICML/NeurIPS workshops; Urban Climate; Physics and Chemistry of the Earth; Mini-Reviews in Medicinal Chemistry; Current Science; F1000Research.

		\textbf{Academic Engagement:}
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item Tsinghua University-Peking University Center for Life Sciences Summer Camp \hfill 2025.07
		\item \begin{tabular}[c]{@{}p{0.8\linewidth}@{}}Shenzhen Bay Laboratory / Shenzhen Medical Academy of Research and Translation Summer Research\end{tabular} \hfill \mbox{2025.07 -- 2025.09}
		\item Tsinghua University Tsien Excellence in Engineering Program -- Zero One Scholar \hfill 2024.06 -- 2027.06
		\item AI Winter School, Brown University Department of Physics \hfill 2025.01
		\item CAAI Artificial Intelligence and Technology Ethics Training Course \hfill 2024.09 -- 2024.12
		\item Fudan University Summer School of Mathematical Logic \hfill 2024.08
		\item Wuhan University National Tianyuan Mathematics Center Discussion Class \hfill 2024.03 -- 2024.06
	\end{itemize}
	
	\vspace{5pt}

	\begin{center}
		\textbf{\large Website Development}
	\end{center}
	\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item \textbf{Peptide Design Competition, Tsinghua University} --- \textcolor{mylinkcolor}{\href{https://www.fbs.frcbs.tsinghua.edu.cn/competition/2025Peptide/}{[Link]}}
		\item \textbf{Polypeptide Structure Database, Tsinghua University} --- \textcolor{mylinkcolor}{\href{https://www.frcbs.tsinghua.edu.cn/cpdb/}{[Link]}}
		\item \textbf{Tong Wang (Tsinghua University) Research Group} --- \textcolor{mylinkcolor}{\href{https://wanggroup.ai/}{[Link]}}
	\end{itemize}

\end{document}
