\documentclass[10pt]{article}
\usepackage{graphicx}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.1cm,top=1.2cm,right=1.1cm,bottom=1.2cm]{geometry}
\usepackage{xcolor}
\usepackage{multicol}

\definecolor{mylinkcolor}{RGB}{0,0,150}
\hypersetup{
	colorlinks=true,
	linkcolor=mylinkcolor,
	filecolor=mylinkcolor,      
	urlcolor=mylinkcolor,
	citecolor=mylinkcolor,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt} 

\begin{document}
	\pagestyle{empty}
	\begin{center}
		\textbf{\Large Yiquan Wang}\\
		\vspace{3pt}
		+86-19537838515 \textbullet \ \href{mailto:ethan@stu.xju.edu.cn}{ethan@stu.xju.edu.cn} \textbullet \ \href{https://wyqmath.cn/}{Personal Homepage} \textbullet \ \href{https://github.com/wyqmath}{GitHub} \textbullet \ \href{https://scholar.google.com/citations?user=ULP3e1cAAAAJ}{Google Scholar} \textbullet \ \href{https://openreview.net/profile?id=~Yiquan_Wang3}{OpenReview} \textbullet \ \href{https://orcid.org/0000-0003-1417-5752}{ORCID} \\
		\vspace{2pt}
		\textit{Research Interests:} Quantitative Biology, Complex Systems, Network Robustness, Statistical Physics \\
		\vspace{2pt}
		\textit{Memberships:} Biophysical Society of China \textbullet \ Chinese Chemical Society \textbullet \ IEEE Biometrics Council \\
		\vspace{-2pt}
		\hrulefill
	\end{center}
	
	\vspace{-2pt}
	\begin{center}
		\textbf{\large Education}
	\end{center}
	\vspace{-4pt}
	\textbf{Xinjiang University (National Base for Mathematical Research and Teaching Talents)} \hfill Urumqi, Xinjiang \\
	\textit{Bachelor of Science in Mathematics and Applied Mathematics} \hfill 2023.09 – 2027.06 
	
	\vspace{2pt}
	\textbf{Tsinghua University \& X-Institute} \hfill Shenzhen, Guangdong \\
	\textit{Tsien Excellence in Engineering Program (Joint Program, X Scholar)} \hfill 2024.06 – 2027.06
	
	\vspace{2pt}
	\begin{center}
		\textbf{\large Research Experience}
	\end{center}
	\vspace{-4pt}
	
	\textbf{First-Principles of Protein Geometry via Mathematical Physics} (Independent Research) \hfill 2025.01 – Present \\
	\textit{Researcher | Mathematical Physics \& Discrete Differential Geometry}
	\begin{itemize}[noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item Abandoned empirical force fields and AI-driven statistical fitting to model protein backbone geometry exclusively through the \textbf{discrete Hasimoto map} and \textbf{nonlinear Schr\"{o}dinger equations}.
		\item Derived exact analytical solutions for local helical transitions, demonstrating sub-Angstrom precision. Proved high cooperativity in phase transitions from a pure kinematic perspective, aligning with the Zimm-Bragg model.
	\end{itemize}
	
	\vspace{2pt}
	\textbf{AI-Driven Biomolecular Dynamics \& Representation Learning} (Tsinghua University ESRT) \hfill 2024.08 – Present \\
	\textit{Project Lead | Supervised by Prof. Kai Wei}
	\begin{itemize}[noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item \textbf{Protein Dynamics Analysis:} Developed a sequence-context-aware decoding framework to robustly reconstruct protein conformational dynamics (thermal fluctuations) directly from crystallographic B-factors.
		\item \textbf{Topological Sequence Representation:} Proposed biological sequence "sonification" (1D to 2D spectrogram mapping), uncovering hidden frequency/topological features to predict protein function, achieving 90.44\% accuracy on the CARE enzyme benchmark (\textbf{Published in JCIM}).
	\end{itemize}
	
	\vspace{2pt}
	\textbf{Network Topology \& System Robustness} (Provincial Innovation Program) \hfill 2024.03 – 2025.06 \\
	\textit{Project Lead | Supervised by Prof. Eminjan Sabir}
	\begin{itemize}[noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item Investigated the \textbf{robustness and fault tolerance} of large-scale topology networks ($k$-ary $n$-cubes) under the Region-Based Fault (RBF) model, moving beyond unrealistic assumptions of independent random noise.
		\item Mathematically proved Hamiltonian connectivity under clustered failure conditions, demonstrating a deep understanding of network resilience and topological invariants in spatially correlated noisy environments.
	\end{itemize}
	
	\vspace{2pt}
	\textbf{Macro-System Dynamics \& Cascading Failures} (CAS Innovation Program) \hfill 2024.11 – 2025.09 \\
	\textit{Project Lead | Supervised by Researcher Yong Ge}
	\begin{itemize}[noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item Constructed a high-fidelity Knowledge Graph (70,297 nodes) to decouple the \textbf{emergence and cascading failures} of compound heatwaves across interconnected physical, biological, and socio-economic networks.
		\item Identified bio-ecological systems as "non-linear amplifiers" of thermal stress, showcasing the ability to abstract and analyze the dynamics of multi-layered complex systems.
	\end{itemize}
	
	\vspace{2pt}
	\textbf{Shenzhen Bay Laboratory} \hfill Shenzhen, Guangdong \\
	\textit{Visiting Student | Institute of Neurological and Psychiatric Disorders (\href{https://www.szbl.ac.cn/research/group/Wen-Yuan.htm}{Wen Yuan's Group})} \hfill 2025.07 – 2025.09
	\begin{itemize}[noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item Investigating the systemic dysregulation of gene regulatory networks in neurological disorders using high-throughput single-cell multi-omics and CRISPR screening.
	\end{itemize}
	
	\vspace{2pt}
	\begin{center}
		\textbf{\large Selected Publications}
	\end{center}
	\vspace{-4pt}
	
	\textbf{Group 1: Mathematical Physics \& First-Principles of Biology}
	\begin{enumerate}[noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt, leftmargin=*, label={[\arabic*]}]
		\item \textbf{Wang, Y.*} (2026). \href{https://arxiv.org/abs/2602.21787}{Spectral entropy of the discrete Hasimoto effective potential exposes sub-residue geometric transitions in protein secondary structure}. \textit{arXiv preprint arXiv:2602.21787}. (Sole \& corresponding author).
		\item \textbf{Wang, Y.*} (2026). \href{https://arxiv.org/abs/2602.16255}{Piecewise integrability of the discrete Hasimoto map for analytic prediction and design of helical peptides}. \textit{arXiv preprint arXiv:2602.16255}. (Sole \& corresponding author).
		\item \textbf{Wang, Y.*} (2026). \href{https://arxiv.org/abs/2602.13160}{Structural barriers of the discrete Hasimoto map applied to protein backbone geometry}. \textit{arXiv preprint arXiv:2602.13160}. (Sole \& corresponding author).
	\end{enumerate}
	
	\vspace{4pt}
	\textbf{Group 2: Biomolecular Dynamics \& Representation Learning} (Showcasing Data \& Engineering Capability)
	\begin{enumerate}[noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt, leftmargin=*, label={[\arabic*]}, resume]
		\item \textbf{Wang, Y.}, Cai, M., Dong, Y., Ma, Y., \& Wei, K. (2025). \href{https://pubs.acs.org/doi/abs/10.1021/acs.jcim.5c01768}{From Signal to Symphony: Exploring 2D Sequence Representations for Protein Function Prediction}. \textit{Journal of Chemical Information and Modeling}, 65(23), 12723-12736. (\textbf{Top}).
		\item \textbf{Wang, Y.*}, Cai, M., Ma, Y., \& Wei, K. (2026). \href{https://openreview.net/forum?id=rTO3JOgC3a}{Sequence-context-aware decoding enables robust reconstruction of protein dynamics from crystallographic B-factors}. \textit{Learning Meaningful Representations of Life (LMRL) Workshop at ICLR 2026}.
		\item \textbf{Wang, Y.}, Ma, Y., Chang, Y., Yan, J., Zhang, J., Cai, M., \& Wei, K. (2025). \href{https://www.mdpi.com/2079-7737/14/12/1665}{Diffusion Models at the Drug Discovery Frontier: A Review on Generating Small Molecules Versus Therapeutic Peptides}. \textit{Biology}, 14(12), 1665.
		\item Wang, X.$^\dagger$, \textbf{Wang, Y.}$^\dagger$, Huang, T.-Y., et al. (2025). \href{https://ieeexplore.ieee.org/abstract/document/11356718/}{Octopus Inspired Optimization: A Hierarchical Framework for Navigating Protein Fitness Landscapes}. \textit{2025 IEEE BIBM}, 6897-6904. (Co-first).
	\end{enumerate}
	
	\vspace{4pt}
	\textbf{Group 3: Complex Systems, Network Topology \& Robustness}
	\begin{enumerate}[noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt, leftmargin=*, label={[\arabic*]}, resume]
		\item \textbf{Wang, Y.}, Liu, Z., Zai, J., Chen, J., \& Sabir, E. (2026). \href{https://ai-2-ase.github.io/papers/CameraReadys\%203-41/24/CameraReady/anonymous-submission-latex-2026.pdf}{Resilient AI Infrastructure by Design: A Spatially-Aware Framework for Tolerating Clustered Failures}. \textit{4th Annual AAAI Workshop on AI to Accelerate Science and Engineering (AI2ASE)}.
		\item \textbf{Wang, Y.*}, Huang, T. Y., Gao, Q., Chang, Y., \& Zhang, J. (2026). \href{https://openreview.net/forum?noteId=rGV8EdrVXE}{AI Driven Discovery of Bio Ecological Mediation in Cascading Heatwave Risks}. \textit{ICLR 2026 Workshop on Foundation Models for Science (FM4Science)}. 
		\item \textbf{Wang, Y.*}, Chang, Y., Zhang, J., et al. (2026). \href{https://openreview.net/forum?id=1x6qbeYHQG}{Geometric Fragility in Alzheimer's Disease: Probing the Loss of Hippocampal Hierarchical Abstraction via Contrastive Point Cloud Modeling}. \textit{LMRL Workshop at ICLR 2026}.
	\end{enumerate}
	
	\vspace{2pt}
	\begin{center}
		\textbf{\large Professional Skills \& Academic Engagement}
	\end{center}
	\vspace{-4pt}
	\begin{itemize}[noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt, leftmargin=*]
		\item \textbf{Technical Skills:} Network Analysis (Graph Theory), Dynamical Systems Modeling, Stochastic Processes, Python, C/C++, MATLAB, Linux, Multi-omics, Molecular Dynamics Simulation.
		\item \textbf{Academic Engagement:} Tsinghua-Peking University Center for Life Sciences Summer Camp (2025); Brown University Department of Physics Artificial Intelligence Winter School (2025); Fudan University Summer School of Mathematical Logic (2024); Wuhan University National Tianyuan Mathematics Center Discussion Class (2024).
		\item \textbf{Selected Awards:} Synthetic Biology Challenges Silver Award $\times$ 2 (2025); Contemporary Undergraduate Mathematical Contest in Modeling (CUMCM) National Second Prize (2025).
	\end{itemize}
	
\end{document}